Literature Review - Informal

### 2019-11-26 Literature Review/Literature Review - Informal/sample.tex
Updated Control section of Literature Review

\documentclass[preprint,8pt]{report}

@@

\maketitle
\tableofcontents

@@

\section{MARL Approaches}

@@

 Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision avoidance problem, similarly from the point of view of differential game theory. They develop a robust feedback system for the robots which they show to be able to drive the system towards predefined targets without interference from other agents. In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent systems

@@

The above discussion has illustrated a few points. The first, and perhaps most important, is that stability is extremely applicable to Multi Agent Reinforcement Learning. This is because of the fact that learning agents, especially in real world environments, are subject to uncertainty and perturbations as well as epsilon-random exploration. As such, it is important that the system is able to return to a stable state after such perturbations. This leads to the need to develop learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge to stable fixed points.

@@

The problem of finding stable solutions through multi agent dynamics also opens the door for a large degree of application domains which are currently quite sparse. I would recommend looking at the contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems control and economic modelling. My particular interest, as always, lies within robotic control problems. This appears to be the most direct and relevant application of stable MAS systems; we can, for instance, use MARL to determine control rules which will lead to stable performance of the system. An example of this might be the problem of Cooperative Moving Path Following Control considered by \cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a pre-defined path without interfering with one another. It is clear then that each player's control is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to determine control rules which lead to stable coordination across the team. Similarly, we can model consider modelling a controller and an adversarial environment as a zero-sum game as examined in \cite{Marden2018AnnualControl}. Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that of Generative adversarial networks (GANs) which can be considered as a two player minimax game with differentiable loss functions.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEfull,references}

>>>>

\documentclass[preprint,11pt]{report}

@@

\maketitle tableofcontents

@@

\section{MARL Approaches} \label{sec::MARL Approaches}

@@

 Mylvaganam et al, in \cite{Mylvaganam2017AutonomousApproach}, consider the N-robot collision
 avoidance problem, similarly from the point of view of differential game theory. They develop a
 robust feedback system for the robots which they show to be able to drive the system towards
 predefined targets whilst providing guarantees of interference from other agents (or lack thereof).
 In \cite{MylvaganamASystems}, Mylvaganam also considers a game theoretic control of multi-agent
 systems in a distributed manner. Here, agents only consider their own payoff structure and have
 limited communication with one another. The author shows that the an approximate equilibrium can be
 found using algebraic methods and illustrate the capabilities of the technique using a collision
 avoidance example. For the sake of brevity, I will not include all of the numerous strides that
 Mylvaganam has introduced to the area. However, I must conclude with those presented in
 \cite{Mylvaganam2014}. Here, the author presents approximate solutions to a number of differential
 games, including linear-quadratic differential games (in which system dynamics are linear functions
 whilst payoff functions are quadratic), Stackelberg differential games, where a hierarchy is
 induced across the players (a notion was suggested in the research proposal) and mean-field games,
 which is discussed in Section \ref{sec::MARL Approaches}. The importance of the linear-quadratic
 differential game is the stability of the solution; solutions for the Nash equilibria are
 admissable iff they are locally exponentially stable (which the author often shows with the aid of
 Lyapunov functions). Approximate solutions to the NE are developed which are more feasible to
 calculate online. The author then shows that this is not simply a theoretical exercise by applying
 the novel methods towards multi-agent collision problems and designs dynamic control laws which
 guarantee that each agent will reach their desired state whilst avoiding collision with the other
 agents. Similarly, the Stackelberg game is applied to the problem of optimal monitoring by a multi
 robot system.

@@

I will briefly summarise the research directions which I develop in this section, to save ourselves
some time, and to preserve sanity. \textbf{I'll do this later. Sanity is overrated.}

The above discussion has illustrated a few points. The first, and perhaps most important, is that
stability is extremely applicable to Stochastic Optimal Control. This is because of the fact
that learning agents, especially in real world environments, are subject to uncertainty and
perturbations as well as epsilon-random exploration. As such, it is important that the system is
able to return to a stable state after such perturbations. This leads to the need to develop
learning systems as in \cite{Letcher2019DifferentiableMechanics} which are attracted to stable
equilibria. Similarly, it allows us to consider existing algorithms and whether they lead to stable
equilibria. For instance, Letcher et al show in \cite{LetcherSTABLEGAMES} that the Learning with
Opponent Learning Awareness (LOLA) algorithm \cite{Foerster2018LearningAwareness} does not converge
to stable fixed points.

@@

The problem of finding stable solutions through multi agent dynamics also opens the door for a large
degree of application domains which are currently quite sparse. I would recommend looking at the
contents page of \cite{Hamalainen1991DifferentialFinland} which illustrates a number of applications
of dynamic and differential game theory in a number of domains including: pursuit-evasion, systems
control and economic modelling. My particular interest, as always, lies within robotic control
problems. This appears to be the most direct and relevant application of stable MAS systems. An
example of this might be the problem of Cooperative Moving Path Following Control considered by
\cite{Reis2019RobustVehicles}. Here, multiple agents must track moving targets according to a
pre-defined path without interfering with one another. It is clear then that each player's control
is dependent on the other and so can be modelled as a game theoretic problem. Our task, then, is to
determine control rules which lead to stable coordination across the team. Similarly, we can model
consider modelling a controller and an adversarial environment as a zero-sum game as examined in
\cite{Marden2018AnnualControl}.

Another application is proposed by Letcher et al in \cite{Letcher2019DifferentiableMechanics} - that
of Generative adversarial networks (GANs) which can be considered as a two player minimax game with
differentiable loss functions. As pointed out by Mylvaganam, it may also be interesting to consider
the differential game problem from the point of view of different information structures. In
real-world systems, it is unlikely that all agents will have access to the information of other
agent' cost functions and current positions. It could, however, be interesting to explore the use of
localisation methods to determine and track this information through observation (e.g. through
Kalman or Bayesian methods). Finally, most of the relevant work in stochastic optimal control
considers the case where system dynamics are linear. A whole new set of problems arise in the more
realistic case where we must consider the non-linearity of system dynamics. Such a consideration
would also allow us to extend these technique to the more difficult (and important) problems in
control.

@@

\bibliographystyle{IEEEtran}

\bibliography{IEEEfull,references}
